---
title: 'ECNS 491 Project: Draft Exploratory Analysis'
author: "Landon Sielaff"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
rm(list=ls())
library(tmap)
library(tidyverse)
library(sf)
library(gtools)
```

```{r}
setwd("/Users/landonsielaff/Downloads/ECNS 491/Deer_and_Elk_Hunting_Districts_(2022_and_2023_Seasons)")
Deer_and_Elk_Hunting_Districts = st_read("Deer_and_Elk_Hunting_Districts_(2022_and_2023_Seasons).shp")

setwd("/Users/landonsielaff/Downloads/ECNS 491/Harvest Data")
harvest =read.csv("fwpHarvestEstimatesReport_Elk.csv")
```
# Wrangle and Cleaning

##### Separating Each Years Data Into It's Own Data Frame

```{r}
for(i in unique(harvest$License.Year)){
  for(j in c("R", "N", "SUM")){
    assign(paste0("harvest_", i,"_", j), harvest |> filter(License.Year == i) |> filter(Residency == j))
  }
}
```

##### Creating a Data Frame that Contains the Index of Each Hunting District for Each Year, Separated by Residents, Non-Residents and Sum

```{r}
hd = na.omit(sort(Deer_and_Elk_Hunting_Districts$DISTRICT, decreasing = F))

harvest_index = data.frame(hd)
colnames(harvest_index) = c("hunting district")

index_match = function(u)
{
  temp = rep(0,length(hd))
  for (i in 1:length(temp)){
    temp[i] =  match(hd[i], u)
  }
  return(temp)
}

harvest_index$index_2004_R = index_match(harvest_2004_R$Hunting.District)
harvest_index$index_2005_R = index_match(harvest_2005_R$Hunting.District)
harvest_index$index_2006_R = index_match(harvest_2006_R$Hunting.District)
harvest_index$index_2007_R = index_match(harvest_2007_R$Hunting.District)
harvest_index$index_2008_R = index_match(harvest_2008_R$Hunting.District)
harvest_index$index_2009_R = index_match(harvest_2009_R$Hunting.District)
harvest_index$index_2010_R = index_match(harvest_2010_R$Hunting.District)
harvest_index$index_2011_R = index_match(harvest_2011_R$Hunting.District)
harvest_index$index_2012_R = index_match(harvest_2012_R$Hunting.District)
harvest_index$index_2013_R = index_match(harvest_2013_R$Hunting.District)
harvest_index$index_2014_R = index_match(harvest_2014_R$Hunting.District)
harvest_index$index_2015_R = index_match(harvest_2015_R$Hunting.District)
harvest_index$index_2016_R = index_match(harvest_2016_R$Hunting.District)
harvest_index$index_2017_R = index_match(harvest_2017_R$Hunting.District)
harvest_index$index_2018_R = index_match(harvest_2018_R$Hunting.District)
harvest_index$index_2019_R = index_match(harvest_2019_R$Hunting.District)
harvest_index$index_2020_R = index_match(harvest_2020_R$Hunting.District)
harvest_index$index_2021_R = index_match(harvest_2021_R$Hunting.District)

harvest_index$index_2004_N = index_match(harvest_2004_N$Hunting.District)
harvest_index$index_2005_N = index_match(harvest_2005_N$Hunting.District)
harvest_index$index_2006_N = index_match(harvest_2006_N$Hunting.District)
harvest_index$index_2007_N = index_match(harvest_2007_N$Hunting.District)
harvest_index$index_2008_N = index_match(harvest_2008_N$Hunting.District)
harvest_index$index_2009_N = index_match(harvest_2009_N$Hunting.District)
harvest_index$index_2010_N = index_match(harvest_2010_N$Hunting.District)
harvest_index$index_2011_N = index_match(harvest_2011_N$Hunting.District)
harvest_index$index_2012_N = index_match(harvest_2012_N$Hunting.District)
harvest_index$index_2013_N = index_match(harvest_2013_N$Hunting.District)
harvest_index$index_2014_N = index_match(harvest_2014_N$Hunting.District)
harvest_index$index_2015_N = index_match(harvest_2015_N$Hunting.District)
harvest_index$index_2016_N = index_match(harvest_2016_N$Hunting.District)
harvest_index$index_2017_N = index_match(harvest_2017_N$Hunting.District)
harvest_index$index_2018_N = index_match(harvest_2018_N$Hunting.District)
harvest_index$index_2019_N = index_match(harvest_2019_N$Hunting.District)
harvest_index$index_2020_N = index_match(harvest_2020_N$Hunting.District)
harvest_index$index_2021_N = index_match(harvest_2021_N$Hunting.District)

harvest_index$index_2004_SUM = index_match(harvest_2004_SUM$Hunting.District)
harvest_index$index_2005_SUM = index_match(harvest_2005_SUM$Hunting.District)
harvest_index$index_2006_SUM = index_match(harvest_2006_SUM$Hunting.District)
harvest_index$index_2007_SUM = index_match(harvest_2007_SUM$Hunting.District)
harvest_index$index_2008_SUM = index_match(harvest_2008_SUM$Hunting.District)
harvest_index$index_2009_SUM = index_match(harvest_2009_SUM$Hunting.District)
harvest_index$index_2010_SUM = index_match(harvest_2010_SUM$Hunting.District)
harvest_index$index_2011_SUM = index_match(harvest_2011_SUM$Hunting.District)
harvest_index$index_2012_SUM = index_match(harvest_2012_SUM$Hunting.District)
harvest_index$index_2013_SUM = index_match(harvest_2013_SUM$Hunting.District)
harvest_index$index_2014_SUM = index_match(harvest_2014_SUM$Hunting.District)
harvest_index$index_2015_SUM = index_match(harvest_2015_SUM$Hunting.District)
harvest_index$index_2016_SUM = index_match(harvest_2016_SUM$Hunting.District)
harvest_index$index_2017_SUM = index_match(harvest_2017_SUM$Hunting.District)
harvest_index$index_2018_SUM = index_match(harvest_2018_SUM$Hunting.District)
harvest_index$index_2019_SUM = index_match(harvest_2019_SUM$Hunting.District)
harvest_index$index_2020_SUM = index_match(harvest_2020_SUM$Hunting.District)
harvest_index$index_2021_SUM = index_match(harvest_2021_SUM$Hunting.District)
```

##### Creating Hunters Data Frame

```{r}
harvest_analysis_Hunters = data.frame(hd)
colnames(harvest_analysis_Hunters) = c("hunting district")

harvest_analysis_Hunters$SUM_2004 = harvest_2004_SUM$Hunters[harvest_index$index_2004_SUM]
harvest_analysis_Hunters$SUM_2005 = harvest_2005_SUM$Hunters[harvest_index$index_2005_SUM]
harvest_analysis_Hunters$SUM_2006 = harvest_2006_SUM$Hunters[harvest_index$index_2006_SUM]
harvest_analysis_Hunters$SUM_2007 = harvest_2007_SUM$Hunters[harvest_index$index_2007_SUM]
harvest_analysis_Hunters$SUM_2008 = harvest_2008_SUM$Hunters[harvest_index$index_2008_SUM]
harvest_analysis_Hunters$SUM_2009 = harvest_2009_SUM$Hunters[harvest_index$index_2009_SUM]
harvest_analysis_Hunters$SUM_2010 = harvest_2010_SUM$Hunters[harvest_index$index_2010_SUM]
harvest_analysis_Hunters$SUM_2011 = harvest_2011_SUM$Hunters[harvest_index$index_2011_SUM]
harvest_analysis_Hunters$SUM_2012 = harvest_2012_SUM$Hunters[harvest_index$index_2012_SUM]
harvest_analysis_Hunters$SUM_2013 = harvest_2013_SUM$Hunters[harvest_index$index_2013_SUM]
harvest_analysis_Hunters$SUM_2014 = harvest_2014_SUM$Hunters[harvest_index$index_2014_SUM]
harvest_analysis_Hunters$SUM_2015 = harvest_2015_SUM$Hunters[harvest_index$index_2015_SUM]
harvest_analysis_Hunters$SUM_2016 = harvest_2016_SUM$Hunters[harvest_index$index_2016_SUM]
harvest_analysis_Hunters$SUM_2017 = harvest_2017_SUM$Hunters[harvest_index$index_2017_SUM]
harvest_analysis_Hunters$SUM_2018 = harvest_2018_SUM$Hunters[harvest_index$index_2018_SUM]
harvest_analysis_Hunters$SUM_2019 = harvest_2019_SUM$Hunters[harvest_index$index_2019_SUM]
harvest_analysis_Hunters$SUM_2020 = harvest_2020_SUM$Hunters[harvest_index$index_2020_SUM]
harvest_analysis_Hunters$SUM_2021 = harvest_2021_SUM$Hunters[harvest_index$index_2021_SUM]
```

##### Creating Total Harvest Data Frame

```{r}
harvest_analysis_Total_Harvest = data.frame(hd)
colnames(harvest_analysis_Total_Harvest) = c("hunting district")

harvest_analysis_Total_Harvest$SUM_2004 = harvest_2004_SUM$Total.Harvest[harvest_index$index_2004_SUM]
harvest_analysis_Total_Harvest$SUM_2005 = harvest_2005_SUM$Total.Harvest[harvest_index$index_2005_SUM]
harvest_analysis_Total_Harvest$SUM_2006 = harvest_2006_SUM$Total.Harvest[harvest_index$index_2006_SUM]
harvest_analysis_Total_Harvest$SUM_2007 = harvest_2007_SUM$Total.Harvest[harvest_index$index_2007_SUM]
harvest_analysis_Total_Harvest$SUM_2008 = harvest_2008_SUM$Total.Harvest[harvest_index$index_2008_SUM]
harvest_analysis_Total_Harvest$SUM_2009 = harvest_2009_SUM$Total.Harvest[harvest_index$index_2009_SUM]
harvest_analysis_Total_Harvest$SUM_2010 = harvest_2010_SUM$Total.Harvest[harvest_index$index_2010_SUM]
harvest_analysis_Total_Harvest$SUM_2011 = harvest_2011_SUM$Total.Harvest[harvest_index$index_2011_SUM]
harvest_analysis_Total_Harvest$SUM_2012 = harvest_2012_SUM$Total.Harvest[harvest_index$index_2012_SUM]
harvest_analysis_Total_Harvest$SUM_2013 = harvest_2013_SUM$Total.Harvest[harvest_index$index_2013_SUM]
harvest_analysis_Total_Harvest$SUM_2014 = harvest_2014_SUM$Total.Harvest[harvest_index$index_2014_SUM]
harvest_analysis_Total_Harvest$SUM_2015 = harvest_2015_SUM$Total.Harvest[harvest_index$index_2015_SUM]
harvest_analysis_Total_Harvest$SUM_2016 = harvest_2016_SUM$Total.Harvest[harvest_index$index_2016_SUM]
harvest_analysis_Total_Harvest$SUM_2017 = harvest_2017_SUM$Total.Harvest[harvest_index$index_2017_SUM]
harvest_analysis_Total_Harvest$SUM_2018 = harvest_2018_SUM$Total.Harvest[harvest_index$index_2018_SUM]
harvest_analysis_Total_Harvest$SUM_2019 = harvest_2019_SUM$Total.Harvest[harvest_index$index_2019_SUM]
harvest_analysis_Total_Harvest$SUM_2020 = harvest_2020_SUM$Total.Harvest[harvest_index$index_2020_SUM]
harvest_analysis_Total_Harvest$SUM_2021 = harvest_2021_SUM$Total.Harvest[harvest_index$index_2021_SUM]
```

##### Creating Bulls Data Frame

```{r}
harvest_analysis_Bulls = data.frame(hd)
colnames(harvest_analysis_Bulls) = c("hunting district")

harvest_analysis_Bulls$SUM_2004 = harvest_2004_SUM$Bulls[harvest_index$index_2004_SUM]
harvest_analysis_Bulls$SUM_2005 = harvest_2005_SUM$Bulls[harvest_index$index_2005_SUM]
harvest_analysis_Bulls$SUM_2006 = harvest_2006_SUM$Bulls[harvest_index$index_2006_SUM]
harvest_analysis_Bulls$SUM_2007 = harvest_2007_SUM$Bulls[harvest_index$index_2007_SUM]
harvest_analysis_Bulls$SUM_2008 = harvest_2008_SUM$Bulls[harvest_index$index_2008_SUM]
harvest_analysis_Bulls$SUM_2009 = harvest_2009_SUM$Bulls[harvest_index$index_2009_SUM]
harvest_analysis_Bulls$SUM_2010 = harvest_2010_SUM$Bulls[harvest_index$index_2010_SUM]
harvest_analysis_Bulls$SUM_2011 = harvest_2011_SUM$Bulls[harvest_index$index_2011_SUM]
harvest_analysis_Bulls$SUM_2012 = harvest_2012_SUM$Bulls[harvest_index$index_2012_SUM]
harvest_analysis_Bulls$SUM_2013 = harvest_2013_SUM$Bulls[harvest_index$index_2013_SUM]
harvest_analysis_Bulls$SUM_2014 = harvest_2014_SUM$Bulls[harvest_index$index_2014_SUM]
harvest_analysis_Bulls$SUM_2015 = harvest_2015_SUM$Bulls[harvest_index$index_2015_SUM]
harvest_analysis_Bulls$SUM_2016 = harvest_2016_SUM$Bulls[harvest_index$index_2016_SUM]
harvest_analysis_Bulls$SUM_2017 = harvest_2017_SUM$Bulls[harvest_index$index_2017_SUM]
harvest_analysis_Bulls$SUM_2018 = harvest_2018_SUM$Bulls[harvest_index$index_2018_SUM]
harvest_analysis_Bulls$SUM_2019 = harvest_2019_SUM$Bulls[harvest_index$index_2019_SUM]
harvest_analysis_Bulls$SUM_2020 = harvest_2020_SUM$Bulls[harvest_index$index_2020_SUM]
harvest_analysis_Bulls$SUM_2021 = harvest_2021_SUM$Bulls[harvest_index$index_2021_SUM]
```

##### Creating 6 or more points Data Frame

```{r}
harvest_analysis_X6orMorePoints = data.frame(hd)
colnames(harvest_analysis_X6orMorePoints) = c("hunting district")

harvest_analysis_X6orMorePoints$SUM_2004 = harvest_2004_SUM$X6.or.More.Points[harvest_index$index_2004_SUM]
harvest_analysis_X6orMorePoints$SUM_2005 = harvest_2005_SUM$X6.or.More.Points[harvest_index$index_2005_SUM]
harvest_analysis_X6orMorePoints$SUM_2006 = harvest_2006_SUM$X6.or.More.Points[harvest_index$index_2006_SUM]
harvest_analysis_X6orMorePoints$SUM_2007 = harvest_2007_SUM$X6.or.More.Points[harvest_index$index_2007_SUM]
harvest_analysis_X6orMorePoints$SUM_2008 = harvest_2008_SUM$X6.or.More.Points[harvest_index$index_2008_SUM]
harvest_analysis_X6orMorePoints$SUM_2009 = harvest_2009_SUM$X6.or.More.Points[harvest_index$index_2009_SUM]
harvest_analysis_X6orMorePoints$SUM_2010 = harvest_2010_SUM$X6.or.More.Points[harvest_index$index_2010_SUM]
harvest_analysis_X6orMorePoints$SUM_2011 = harvest_2011_SUM$X6.or.More.Points[harvest_index$index_2011_SUM]
harvest_analysis_X6orMorePoints$SUM_2012 = harvest_2012_SUM$X6.or.More.Points[harvest_index$index_2012_SUM]
harvest_analysis_X6orMorePoints$SUM_2013 = harvest_2013_SUM$X6.or.More.Points[harvest_index$index_2013_SUM]
harvest_analysis_X6orMorePoints$SUM_2014 = harvest_2014_SUM$X6.or.More.Points[harvest_index$index_2014_SUM]
harvest_analysis_X6orMorePoints$SUM_2015 = harvest_2015_SUM$X6.or.More.Points[harvest_index$index_2015_SUM]
harvest_analysis_X6orMorePoints$SUM_2016 = harvest_2016_SUM$X6.or.More.Points[harvest_index$index_2016_SUM]
harvest_analysis_X6orMorePoints$SUM_2017 = harvest_2017_SUM$X6.or.More.Points[harvest_index$index_2017_SUM]
harvest_analysis_X6orMorePoints$SUM_2018 = harvest_2018_SUM$X6.or.More.Points[harvest_index$index_2018_SUM]
harvest_analysis_X6orMorePoints$SUM_2019 = harvest_2019_SUM$X6.or.More.Points[harvest_index$index_2019_SUM]
harvest_analysis_X6orMorePoints$SUM_2020 = harvest_2020_SUM$X6.or.More.Points[harvest_index$index_2020_SUM]
harvest_analysis_X6orMorePoints$SUM_2021 = harvest_2021_SUM$X6.or.More.Points[harvest_index$index_2021_SUM]
```

##### Creating Bow Data Frame

```{r}
harvest_analysis_Bow = data.frame(na.omit(sort(Deer_and_Elk_Hunting_Districts$DISTRICT, decreasing = F)))
colnames(harvest_analysis_Bow) = c("hunting district")

harvest_analysis_Bow$SUM_2004 = harvest_2004_SUM$Bow[harvest_index$index_2004_SUM]
harvest_analysis_Bow$SUM_2005 = harvest_2005_SUM$Bow[harvest_index$index_2005_SUM]
harvest_analysis_Bow$SUM_2006 = harvest_2006_SUM$Bow[harvest_index$index_2006_SUM]
harvest_analysis_Bow$SUM_2007 = harvest_2007_SUM$Bow[harvest_index$index_2007_SUM]
harvest_analysis_Bow$SUM_2008 = harvest_2008_SUM$Bow[harvest_index$index_2008_SUM]
harvest_analysis_Bow$SUM_2009 = harvest_2009_SUM$Bow[harvest_index$index_2009_SUM]
harvest_analysis_Bow$SUM_2010 = harvest_2010_SUM$Bow[harvest_index$index_2010_SUM]
harvest_analysis_Bow$SUM_2011 = harvest_2011_SUM$Bow[harvest_index$index_2011_SUM]
harvest_analysis_Bow$SUM_2012 = harvest_2012_SUM$Bow[harvest_index$index_2012_SUM]
harvest_analysis_Bow$SUM_2013 = harvest_2013_SUM$Bow[harvest_index$index_2013_SUM]
harvest_analysis_Bow$SUM_2014 = harvest_2014_SUM$Bow[harvest_index$index_2014_SUM]
harvest_analysis_Bow$SUM_2015 = harvest_2015_SUM$Bow[harvest_index$index_2015_SUM]
harvest_analysis_Bow$SUM_2016 = harvest_2016_SUM$Bow[harvest_index$index_2016_SUM]
harvest_analysis_Bow$SUM_2017 = harvest_2017_SUM$Bow[harvest_index$index_2017_SUM]
harvest_analysis_Bow$SUM_2018 = harvest_2018_SUM$Bow[harvest_index$index_2018_SUM]
harvest_analysis_Bow$SUM_2019 = harvest_2019_SUM$Bow[harvest_index$index_2019_SUM]
harvest_analysis_Bow$SUM_2020 = harvest_2020_SUM$Bow[harvest_index$index_2020_SUM]
harvest_analysis_Bow$SUM_2021 = harvest_2021_SUM$Bow[harvest_index$index_2021_SUM]
```

##### Creating Rifle Data Frame

```{r}
harvest_analysis_Rifle = data.frame(hd)
colnames(harvest_analysis_Rifle) = c("hunting district")

harvest_analysis_Rifle$SUM_2004 = harvest_2004_SUM$Rifle[harvest_index$index_2004_SUM]
harvest_analysis_Rifle$SUM_2005 = harvest_2005_SUM$Rifle[harvest_index$index_2005_SUM]
harvest_analysis_Rifle$SUM_2006 = harvest_2006_SUM$Rifle[harvest_index$index_2006_SUM]
harvest_analysis_Rifle$SUM_2007 = harvest_2007_SUM$Rifle[harvest_index$index_2007_SUM]
harvest_analysis_Rifle$SUM_2008 = harvest_2008_SUM$Rifle[harvest_index$index_2008_SUM]
harvest_analysis_Rifle$SUM_2009 = harvest_2009_SUM$Rifle[harvest_index$index_2009_SUM]
harvest_analysis_Rifle$SUM_2010 = harvest_2010_SUM$Rifle[harvest_index$index_2010_SUM]
harvest_analysis_Rifle$SUM_2011 = harvest_2011_SUM$Rifle[harvest_index$index_2011_SUM]
harvest_analysis_Rifle$SUM_2012 = harvest_2012_SUM$Rifle[harvest_index$index_2012_SUM]
harvest_analysis_Rifle$SUM_2013 = harvest_2013_SUM$Rifle[harvest_index$index_2013_SUM]
harvest_analysis_Rifle$SUM_2014 = harvest_2014_SUM$Rifle[harvest_index$index_2014_SUM]
harvest_analysis_Rifle$SUM_2015 = harvest_2015_SUM$Rifle[harvest_index$index_2015_SUM]
harvest_analysis_Rifle$SUM_2016 = harvest_2016_SUM$Rifle[harvest_index$index_2016_SUM]
harvest_analysis_Rifle$SUM_2017 = harvest_2017_SUM$Rifle[harvest_index$index_2017_SUM]
harvest_analysis_Rifle$SUM_2018 = harvest_2018_SUM$Rifle[harvest_index$index_2018_SUM]
harvest_analysis_Rifle$SUM_2019 = harvest_2019_SUM$Rifle[harvest_index$index_2019_SUM]
harvest_analysis_Rifle$SUM_2020 = harvest_2020_SUM$Rifle[harvest_index$index_2020_SUM]
harvest_analysis_Rifle$SUM_2021 = harvest_2021_SUM$Rifle[harvest_index$index_2021_SUM]
```

##### Creating Days Per Hunter Data Frame

```{r}
harvest_analysis_DaysPerHunter = data.frame(hd)
colnames(harvest_analysis_DaysPerHunter) = c("hunting district")

harvest_analysis_DaysPerHunter$SUM_2004 = harvest_2004_SUM$Days.per.Hunter[harvest_index$index_2004_SUM]
harvest_analysis_DaysPerHunter$SUM_2005 = harvest_2005_SUM$Days.per.Hunter[harvest_index$index_2005_SUM]
harvest_analysis_DaysPerHunter$SUM_2006 = harvest_2006_SUM$Days.per.Hunter[harvest_index$index_2006_SUM]
harvest_analysis_DaysPerHunter$SUM_2007 = harvest_2007_SUM$Days.per.Hunter[harvest_index$index_2007_SUM]
harvest_analysis_DaysPerHunter$SUM_2008 = harvest_2008_SUM$Days.per.Hunter[harvest_index$index_2008_SUM]
harvest_analysis_DaysPerHunter$SUM_2009 = harvest_2009_SUM$Days.per.Hunter[harvest_index$index_2009_SUM]
harvest_analysis_DaysPerHunter$SUM_2010 = harvest_2010_SUM$Days.per.Hunter[harvest_index$index_2010_SUM]
harvest_analysis_DaysPerHunter$SUM_2011 = harvest_2011_SUM$Days.per.Hunter[harvest_index$index_2011_SUM]
harvest_analysis_DaysPerHunter$SUM_2012 = harvest_2012_SUM$Days.per.Hunter[harvest_index$index_2012_SUM]
harvest_analysis_DaysPerHunter$SUM_2013 = harvest_2013_SUM$Days.per.Hunter[harvest_index$index_2013_SUM]
harvest_analysis_DaysPerHunter$SUM_2014 = harvest_2014_SUM$Days.per.Hunter[harvest_index$index_2014_SUM]
harvest_analysis_DaysPerHunter$SUM_2015 = harvest_2015_SUM$Days.per.Hunter[harvest_index$index_2015_SUM]
harvest_analysis_DaysPerHunter$SUM_2016 = harvest_2016_SUM$Days.per.Hunter[harvest_index$index_2016_SUM]
harvest_analysis_DaysPerHunter$SUM_2017 = harvest_2017_SUM$Days.per.Hunter[harvest_index$index_2017_SUM]
harvest_analysis_DaysPerHunter$SUM_2018 = harvest_2018_SUM$Days.per.Hunter[harvest_index$index_2018_SUM]
harvest_analysis_DaysPerHunter$SUM_2019 = harvest_2019_SUM$Days.per.Hunter[harvest_index$index_2019_SUM]
harvest_analysis_DaysPerHunter$SUM_2020 = harvest_2020_SUM$Days.per.Hunter[harvest_index$index_2020_SUM]
harvest_analysis_DaysPerHunter$SUM_2021 = harvest_2021_SUM$Days.per.Hunter[harvest_index$index_2021_SUM]
```

##### Generating Graphics for Hunter Analysis

```{r}
hunters_graphics = Deer_and_Elk_Hunting_Districts
hunters_graphics$Hunters_2004 = harvest_analysis_Hunters$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2005 = harvest_analysis_Hunters$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2006 = harvest_analysis_Hunters$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2007 = harvest_analysis_Hunters$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2008 = harvest_analysis_Hunters$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2009 = harvest_analysis_Hunters$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2010 = harvest_analysis_Hunters$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2011 = harvest_analysis_Hunters$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2012 = harvest_analysis_Hunters$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2013 = harvest_analysis_Hunters$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2014 = harvest_analysis_Hunters$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2015 = harvest_analysis_Hunters$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2016 = harvest_analysis_Hunters$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2017 = harvest_analysis_Hunters$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2018 = harvest_analysis_Hunters$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2019 = harvest_analysis_Hunters$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2020 = harvest_analysis_Hunters$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
hunters_graphics$Hunters_2021 = harvest_analysis_Hunters$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Hunters$`hunting district`)]
```

##### Generating Graphics for Total Harvest Analysis

```{r}
harvest_graphics = Deer_and_Elk_Hunting_Districts
harvest_graphics$Total_Harvests_2004 = harvest_analysis_Total_Harvest$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2005 = harvest_analysis_Total_Harvest$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2006 = harvest_analysis_Total_Harvest$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2007 = harvest_analysis_Total_Harvest$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2008 = harvest_analysis_Total_Harvest$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2009 = harvest_analysis_Total_Harvest$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2010 = harvest_analysis_Total_Harvest$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2011 = harvest_analysis_Total_Harvest$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2012 = harvest_analysis_Total_Harvest$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2013 = harvest_analysis_Total_Harvest$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2014 = harvest_analysis_Total_Harvest$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2015 = harvest_analysis_Total_Harvest$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2016 = harvest_analysis_Total_Harvest$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2017 = harvest_analysis_Total_Harvest$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2018 = harvest_analysis_Total_Harvest$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2019 = harvest_analysis_Total_Harvest$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2020 = harvest_analysis_Total_Harvest$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
harvest_graphics$Total_Harvests_2021 = harvest_analysis_Total_Harvest$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Total_Harvest$`hunting district`)]
```

##### Generating Graphics for Bull Analysis

```{r}
bull_graphics = Deer_and_Elk_Hunting_Districts
bull_graphics$Bulls_2004 = harvest_analysis_Bulls$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2005 = harvest_analysis_Bulls$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2006 = harvest_analysis_Bulls$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2007 = harvest_analysis_Bulls$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2008 = harvest_analysis_Bulls$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2009 = harvest_analysis_Bulls$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2010 = harvest_analysis_Bulls$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2011 = harvest_analysis_Bulls$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2012 = harvest_analysis_Bulls$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2013 = harvest_analysis_Bulls$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2014 = harvest_analysis_Bulls$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2015 = harvest_analysis_Bulls$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2016 = harvest_analysis_Bulls$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2017 = harvest_analysis_Bulls$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2018 = harvest_analysis_Bulls$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2019 = harvest_analysis_Bulls$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2020 = harvest_analysis_Bulls$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
bull_graphics$Bulls_2021 = harvest_analysis_Bulls$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bulls$`hunting district`)]
```

##### Generating Graphics for 6 or More Points Analysis

```{r}
x6ormore_graphics = Deer_and_Elk_Hunting_Districts
x6ormore_graphics$X6orMorePoints_2004 = harvest_analysis_X6orMorePoints$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2005 = harvest_analysis_X6orMorePoints$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2006 = harvest_analysis_X6orMorePoints$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2007 = harvest_analysis_X6orMorePoints$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2008 = harvest_analysis_X6orMorePoints$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2009 = harvest_analysis_X6orMorePoints$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2010 = harvest_analysis_X6orMorePoints$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2011 = harvest_analysis_X6orMorePoints$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2012 = harvest_analysis_X6orMorePoints$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2013 = harvest_analysis_X6orMorePoints$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2014 = harvest_analysis_X6orMorePoints$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2015 = harvest_analysis_X6orMorePoints$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2016 = harvest_analysis_X6orMorePoints$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2017 = harvest_analysis_X6orMorePoints$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2018 = harvest_analysis_X6orMorePoints$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2019 = harvest_analysis_X6orMorePoints$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2020 = harvest_analysis_X6orMorePoints$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
x6ormore_graphics$X6orMorePoints_2021 = harvest_analysis_X6orMorePoints$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_X6orMorePoints$`hunting district`)]
```

##### Generating Graphics for Bow Analysis

```{r}
bow_graphics = Deer_and_Elk_Hunting_Districts
bow_graphics$Bow_2004 = harvest_analysis_Bow$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2005 = harvest_analysis_Bow$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2006 = harvest_analysis_Bow$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2007 = harvest_analysis_Bow$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2008 = harvest_analysis_Bow$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2009 = harvest_analysis_Bow$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2010 = harvest_analysis_Bow$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2011 = harvest_analysis_Bow$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2012 = harvest_analysis_Bow$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2013 = harvest_analysis_Bow$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2014 = harvest_analysis_Bow$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2015 = harvest_analysis_Bow$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2016 = harvest_analysis_Bow$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2017 = harvest_analysis_Bow$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2018 = harvest_analysis_Bow$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2019 = harvest_analysis_Bow$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2020 = harvest_analysis_Bow$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
bow_graphics$Bow_2021 = harvest_analysis_Bow$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Bow$`hunting district`)]
```

##### Generating Graphics for Rifle Analysis

```{r}
rifle_graphics = Deer_and_Elk_Hunting_Districts
rifle_graphics$Rifle_2004 = harvest_analysis_Rifle$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2005 = harvest_analysis_Rifle$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2006 = harvest_analysis_Rifle$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2007 = harvest_analysis_Rifle$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2008 = harvest_analysis_Rifle$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2009 = harvest_analysis_Rifle$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2010 = harvest_analysis_Rifle$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2011 = harvest_analysis_Rifle$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2012 = harvest_analysis_Rifle$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2013 = harvest_analysis_Rifle$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2014 = harvest_analysis_Rifle$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2015 = harvest_analysis_Rifle$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2016 = harvest_analysis_Rifle$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2017 = harvest_analysis_Rifle$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2018 = harvest_analysis_Rifle$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2019 = harvest_analysis_Rifle$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2020 = harvest_analysis_Rifle$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
rifle_graphics$Rifle_2021 = harvest_analysis_Rifle$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_Rifle$`hunting district`)]
```

##### Generating Graphics for Days per Hunter Analysis

```{r}
daysperhunter_graphics = Deer_and_Elk_Hunting_Districts
daysperhunter_graphics$DaysPerHunter_2004 = harvest_analysis_DaysPerHunter$SUM_2004[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2005 = harvest_analysis_DaysPerHunter$SUM_2005[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2006 = harvest_analysis_DaysPerHunter$SUM_2006[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2007 = harvest_analysis_DaysPerHunter$SUM_2007[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2008 = harvest_analysis_DaysPerHunter$SUM_2008[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2009 = harvest_analysis_DaysPerHunter$SUM_2009[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2010 = harvest_analysis_DaysPerHunter$SUM_2010[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2011 = harvest_analysis_DaysPerHunter$SUM_2011[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2012 = harvest_analysis_DaysPerHunter$SUM_2012[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2013 = harvest_analysis_DaysPerHunter$SUM_2013[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2014 = harvest_analysis_DaysPerHunter$SUM_2014[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2015 = harvest_analysis_DaysPerHunter$SUM_2015[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2016 = harvest_analysis_DaysPerHunter$SUM_2016[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2017 = harvest_analysis_DaysPerHunter$SUM_2017[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2018 = harvest_analysis_DaysPerHunter$SUM_2018[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2019 = harvest_analysis_DaysPerHunter$SUM_2019[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2020 = harvest_analysis_DaysPerHunter$SUM_2020[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
daysperhunter_graphics$DaysPerHunter_2021 = harvest_analysis_DaysPerHunter$SUM_2021[match(Deer_and_Elk_Hunting_Districts$DISTRICT,harvest_analysis_DaysPerHunter$`hunting district`)]
```


# Exploratory Analysis

```
harvest_graphics$means = rep(0, length(harvest_graphics$DISTRICT))
for( i in 1:length(harvest_graphics$DISTRICT)){
  harvest_graphics$means[i] = rowMeans(harvest_graphics$Total_Harvests_2004[i], harvest_graphics$Total_Harvests_2005[i], harvest_graphics$Total_Harvests_2006[i], harvest_graphics$Total_Harvests_2007[i], harvest_graphics$Total_Harvests_2008[i],
                                      harvest_graphics$Total_Harvests_2009[i], harvest_graphics$Total_Harvests_2010[i], harvest_graphics$Total_Harvests_2011[i], harvest_graphics$Total_Harvests_2012[i], harvest_graphics$Total_Harvests_2013[i],
                                      harvest_graphics$Total_Harvests_2014[i], harvest_graphics$Total_Harvests_2015[i], harvest_graphics$Total_Harvests_2016[i], harvest_graphics$Total_Harvests_2017[i], harvest_graphics$Total_Harvests_2018[i],
                                      harvest_graphics$Total_Harvests_2019[i], harvest_graphics$Total_Harvests_2020[i], harvest_graphics$Total_Harvests_2021[i], na.rm = TRUE)
}
plot(harvest_graphics["means"])
(best_harvest = head(harvest_graphics %>% select(DISTRICT, means) %>% arrange(desc(means))))

total_harvests = subset(harvest_graphics, select = c(Total_Harvests_2004, Total_Harvests_2005, Total_Harvests_2006, Total_Harvests_2007, Total_Harvests_2008, Total_Harvests_2009, Total_Harvests_2010, Total_Harvests_2011,
                                                     Total_Harvests_2012, Total_Harvests_2013, Total_Harvests_2014, Total_Harvests_2015, Total_Harvests_2016, Total_Harvests_2017, Total_Harvests_2018, Total_Harvests_2019,
                                                     Total_Harvests_2020, Total_Harvests_2021))

colnames(total_harvests) = as.character(c(2004:2021))
rownames(total_harvests) = as.character(harvest_graphics$DISTRICT)
```



##### Looking at the last 5 years of Harvest Data

```{r}
plot(harvest_graphics["Total_Harvests_2017"])
plot(harvest_graphics["Total_Harvests_2018"])
plot(harvest_graphics["Total_Harvests_2019"])
plot(harvest_graphics["Total_Harvests_2020"])
plot(harvest_graphics["Total_Harvests_2021"])

(best_harvest_2017 = head(harvest_graphics %>% select(DISTRICT, Total_Harvests_2017) %>% arrange(desc(Total_Harvests_2017))))
(best_harvest_2018 = head(harvest_graphics %>% select(DISTRICT, Total_Harvests_2018) %>% arrange(desc(Total_Harvests_2018))))
(best_harvest_2019 = head(harvest_graphics %>% select(DISTRICT, Total_Harvests_2019) %>% arrange(desc(Total_Harvests_2019))))
(best_harvest_2020 = head(harvest_graphics %>% select(DISTRICT, Total_Harvests_2020) %>% arrange(desc(Total_Harvests_2020))))
(best_harvest_2021 = head(harvest_graphics %>% select(DISTRICT, Total_Harvests_2021) %>% arrange(desc(Total_Harvests_2021))))
```

##### Looking at the last 5 years of Bull Harvest Data

```{r}
plot(bull_graphics["Bulls_2017"])
plot(bull_graphics["Bulls_2018"])
plot(bull_graphics["Bulls_2019"])
plot(bull_graphics["Bulls_2020"])
plot(bull_graphics["Bulls_2021"])

(best_bull_harvest_2017 = head(bull_graphics %>% select(DISTRICT, Bulls_2017) %>% arrange(desc(Bulls_2017))))
(best_bull_harvest_2018 = head(bull_graphics %>% select(DISTRICT, Bulls_2018) %>% arrange(desc(Bulls_2018))))
(best_bull_harvest_2019 = head(bull_graphics %>% select(DISTRICT, Bulls_2019) %>% arrange(desc(Bulls_2019))))
(best_bull_harvest_2020 = head(bull_graphics %>% select(DISTRICT, Bulls_2020) %>% arrange(desc(Bulls_2020))))
(best_bull_harvest_2021 = head(bull_graphics %>% select(DISTRICT, Bulls_2021) %>% arrange(desc(Bulls_2021))))
```

##### Looking at the last 5 years of 6 or More Points Data

```{r}
plot(x6ormore_graphics["X6orMorePoints_2017"])
plot(x6ormore_graphics["X6orMorePoints_2018"])
plot(x6ormore_graphics["X6orMorePoints_2019"])
plot(x6ormore_graphics["X6orMorePoints_2020"])
plot(x6ormore_graphics["X6orMorePoints_2021"])

(best_x6ormore_harvests_2017 = head(x6ormore_graphics %>% select(DISTRICT, X6orMorePoints_2017) %>% arrange(desc(X6orMorePoints_2017))))
(best_x6ormore_harvests_2018 = head(x6ormore_graphics %>% select(DISTRICT, X6orMorePoints_2018) %>% arrange(desc(X6orMorePoints_2018))))
(best_x6ormore_harvests_2019 = head(x6ormore_graphics %>% select(DISTRICT, X6orMorePoints_2019) %>% arrange(desc(X6orMorePoints_2019))))
(best_x6ormore_harvests_2020 = head(x6ormore_graphics %>% select(DISTRICT, X6orMorePoints_2020) %>% arrange(desc(X6orMorePoints_2020))))
(best_x6ormore_harvests_2021 = head(x6ormore_graphics %>% select(DISTRICT, X6orMorePoints_2021) %>% arrange(desc(X6orMorePoints_2021))))
```


# Write UP

For this project I wanted to look at Montana Fish, Wildlife and Parks public data to determine which hunting districts are the best for elk hunting. This project is important to me because I have always been an avid outdoors man and since moving to Montana, it has been hard for me to put in the time and effort to scout every possible hunting unit to find the best places to hunt. For this project, I first want to complete a descriptive analysis of each of the different hunting districts and regions to first find which ones have the highest harvest rate for bull elk with over 6 points (mature bulls). After completing a descriptive analysis, I then want to merge the harvest reports with both the drawing statistics and hunting district data to find the hunting unit with the highest rate of harvest and highest odds of drawing. An additional analysis that I want to complete is to add in weather, elevation and land ownership type (public vs private) to see how these variables affect and/or are correlated with the harvest statistics. 


• A couple of paragraphs explaining how you processed your data and why you made the choices you did.
Identify the unit of analysis in your cleaned, merged dataset.


• A couple of paragraphs explaining any transformations you applied, how you dealt with any missing
data or extreme values, and why.

• A few pages that describe your findings and show the visualizations.