---
title: 'ECNS 491 Project: Draft Exploratory Analysis'
author: "Landon Sielaff"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
rm(list=ls())
library(tmap)
library(tidyverse)
library(sf)
library(gtools)
library(dplyr)
```

```{r}
setwd("/Users/landonsielaff/Downloads/ECNS 491/gitRepoFinal_Done/MSU_ECNS491_Sielaff/data/Deer_and_Elk_Hunting_Districts_(2022_and_2023_Seasons)")
Deer_and_Elk_Hunting_Districts = st_read("Deer_and_Elk_Hunting_Districts_(2022_and_2023_Seasons).shp")

setwd("/Users/landonsielaff/Downloads/ECNS 491/gitRepoFinal_Done/MSU_ECNS491_Sielaff/data")
harvest =read.csv("fwpHarvestEstimatesReport_Elk.csv")
```
# Wrangle and Cleaning

##### Separating Each Years Data Into It's Own Data Frame

```{r}
for(i in unique(harvest$License.Year)){
  for(j in c("R", "N", "SUM")){
    assign(paste0("harvest_", i,"_", j), harvest |> filter(License.Year == i) |> filter(Residency == j))
  }
}
```

##### Creating a Data Frame that Contains the Index of Each Hunting District for Each Year, Separated by Residents, Non-Residents and Sum

```{r}
hd = na.omit(sort(Deer_and_Elk_Hunting_Districts$DISTRICT, decreasing = F))

harvest_index = data.frame(hd)
colnames(harvest_index) = c("hunting district")

index_match = function(u)
{
  temp = rep(0,length(hd))
  for (i in 1:length(temp)){
    temp[i] =  match(hd[i], u)
  }
  return(temp)
}

harvest_index$index_2004_R = index_match(harvest_2004_R$Hunting.District)
harvest_index$index_2005_R = index_match(harvest_2005_R$Hunting.District)
harvest_index$index_2006_R = index_match(harvest_2006_R$Hunting.District)
harvest_index$index_2007_R = index_match(harvest_2007_R$Hunting.District)
harvest_index$index_2008_R = index_match(harvest_2008_R$Hunting.District)
harvest_index$index_2009_R = index_match(harvest_2009_R$Hunting.District)
harvest_index$index_2010_R = index_match(harvest_2010_R$Hunting.District)
harvest_index$index_2011_R = index_match(harvest_2011_R$Hunting.District)
harvest_index$index_2012_R = index_match(harvest_2012_R$Hunting.District)
harvest_index$index_2013_R = index_match(harvest_2013_R$Hunting.District)
harvest_index$index_2014_R = index_match(harvest_2014_R$Hunting.District)
harvest_index$index_2015_R = index_match(harvest_2015_R$Hunting.District)
harvest_index$index_2016_R = index_match(harvest_2016_R$Hunting.District)
harvest_index$index_2017_R = index_match(harvest_2017_R$Hunting.District)
harvest_index$index_2018_R = index_match(harvest_2018_R$Hunting.District)
harvest_index$index_2019_R = index_match(harvest_2019_R$Hunting.District)
harvest_index$index_2020_R = index_match(harvest_2020_R$Hunting.District)
harvest_index$index_2021_R = index_match(harvest_2021_R$Hunting.District)

harvest_index$index_2004_N = index_match(harvest_2004_N$Hunting.District)
harvest_index$index_2005_N = index_match(harvest_2005_N$Hunting.District)
harvest_index$index_2006_N = index_match(harvest_2006_N$Hunting.District)
harvest_index$index_2007_N = index_match(harvest_2007_N$Hunting.District)
harvest_index$index_2008_N = index_match(harvest_2008_N$Hunting.District)
harvest_index$index_2009_N = index_match(harvest_2009_N$Hunting.District)
harvest_index$index_2010_N = index_match(harvest_2010_N$Hunting.District)
harvest_index$index_2011_N = index_match(harvest_2011_N$Hunting.District)
harvest_index$index_2012_N = index_match(harvest_2012_N$Hunting.District)
harvest_index$index_2013_N = index_match(harvest_2013_N$Hunting.District)
harvest_index$index_2014_N = index_match(harvest_2014_N$Hunting.District)
harvest_index$index_2015_N = index_match(harvest_2015_N$Hunting.District)
harvest_index$index_2016_N = index_match(harvest_2016_N$Hunting.District)
harvest_index$index_2017_N = index_match(harvest_2017_N$Hunting.District)
harvest_index$index_2018_N = index_match(harvest_2018_N$Hunting.District)
harvest_index$index_2019_N = index_match(harvest_2019_N$Hunting.District)
harvest_index$index_2020_N = index_match(harvest_2020_N$Hunting.District)
harvest_index$index_2021_N = index_match(harvest_2021_N$Hunting.District)

harvest_index$index_2004_SUM = index_match(harvest_2004_SUM$Hunting.District)
harvest_index$index_2005_SUM = index_match(harvest_2005_SUM$Hunting.District)
harvest_index$index_2006_SUM = index_match(harvest_2006_SUM$Hunting.District)
harvest_index$index_2007_SUM = index_match(harvest_2007_SUM$Hunting.District)
harvest_index$index_2008_SUM = index_match(harvest_2008_SUM$Hunting.District)
harvest_index$index_2009_SUM = index_match(harvest_2009_SUM$Hunting.District)
harvest_index$index_2010_SUM = index_match(harvest_2010_SUM$Hunting.District)
harvest_index$index_2011_SUM = index_match(harvest_2011_SUM$Hunting.District)
harvest_index$index_2012_SUM = index_match(harvest_2012_SUM$Hunting.District)
harvest_index$index_2013_SUM = index_match(harvest_2013_SUM$Hunting.District)
harvest_index$index_2014_SUM = index_match(harvest_2014_SUM$Hunting.District)
harvest_index$index_2015_SUM = index_match(harvest_2015_SUM$Hunting.District)
harvest_index$index_2016_SUM = index_match(harvest_2016_SUM$Hunting.District)
harvest_index$index_2017_SUM = index_match(harvest_2017_SUM$Hunting.District)
harvest_index$index_2018_SUM = index_match(harvest_2018_SUM$Hunting.District)
harvest_index$index_2019_SUM = index_match(harvest_2019_SUM$Hunting.District)
harvest_index$index_2020_SUM = index_match(harvest_2020_SUM$Hunting.District)
harvest_index$index_2021_SUM = index_match(harvest_2021_SUM$Hunting.District)
```

### Descriptive Analysis

```{r}
districts_2 = harvest |> filter(Hunting.District %in% hd) |> filter(Residency == c("R", "N")) |> filter(Days > 0) #|> select(License.Year ,Hunting.District, Residency, Hunters, Total.Harvest, Bulls, X6.or.More.Points)
yearsum = harvest |> filter(Residency == "SUM") |> filter(Hunting.District == "State")
yearres = harvest |> filter(Residency == "R") |> filter(Hunting.District == "State")
yearn = harvest |> filter(Residency == "N") |> filter(Hunting.District == "State")

# Total amount of Montana residents who have purchased elk tags (2004 - 2021)
sum(yearres$Hunters)

# Total amount of Montana non-residents who have purchased elk tags (2004 - 2021)
sum(yearn$Hunters)

# Average harvest rates for all hunters, residents and non-residents (2004 - 2021)
mean(yearsum$Total.Harvest/yearsum$Hunters)
mean(yearres$Total.Harvest/yearres$Hunters)
mean(yearn$Total.Harvest/yearn$Hunters)

# Average bull harvest rates for all hunters, residents and non-residents (2004 - 2021)
mean(yearsum$Bulls/yearsum$Hunters)
mean(yearres$Bulls/yearres$Hunters)
mean(yearn$Bulls/yearn$Hunters)

# Average bull harvest rates with 6 or more points for all hunters, residents and non-residents (2004 - 2021)
mean(yearsum$X6.or.More.Points/yearsum$Hunters)
mean(yearres$X6.or.More.Points/yearres$Hunters)
mean(yearn$X6.or.More.Points/yearn$Hunters)

# Montana Non_Resident Hunters
ggplot(yearn, aes(x = License.Year, y = Hunters)) + geom_line() +  
  xlab("Year") + 
  ylab("Number of Hunters") +
  ggtitle("Montana Non_Resident Hunters")

# Montana Non-Resident Harvest Rates
ggplot(yearn, aes(x = License.Year, y = Total.Harvest/Hunters)) + geom_line() +  
  xlab("Year") + 
  ylab("Harvest Rate") +
  ggtitle("Montana Non-Resident Harvest Rates") +
  geom_hline(yintercept = mean(yearn$Total.Harvest/yearn$Hunters), color = "red", linetype="dashed")

# Montana Resident Hunters
ggplot(yearres, aes(x = License.Year, y = Hunters)) + geom_line() +  
  xlab("Year") + 
  ylab("Number of Hunters") +
  ggtitle("Montana Resident Hunters")

# Montana Resident Harvest Rate
ggplot(yearres, aes(x = License.Year, y = Total.Harvest/Hunters)) + geom_line() +  
  xlab("Year") + 
  ylab("Harvest Rate") +
  ggtitle("Montana Resident Harvest Rates") +
  geom_hline(yintercept = mean(yearres$Total.Harvest/yearres$Hunters), color = "red", linetype="dashed")

# Montana Resident vs. Non-Resident Days per Hunter
ggplot(districts_2, aes(x = Days.per.Hunter, color = Residency)) + geom_histogram() +  
  ggtitle("Montana Resident vs. Non-Resident Days per Hunter") 

```

##### Creating Non-Residents Hunters Data Frame

```{r}
harvest_analysis_Hunters = data.frame(hd)
colnames(harvest_analysis_Hunters) = c("hunting district")

harvest_analysis_Hunters$N_2004 = harvest_2004_N$Hunters[harvest_index$index_2004_N]
harvest_analysis_Hunters$N_2005 = harvest_2005_N$Hunters[harvest_index$index_2005_N]
harvest_analysis_Hunters$N_2006 = harvest_2006_N$Hunters[harvest_index$index_2006_N]
harvest_analysis_Hunters$N_2007 = harvest_2007_N$Hunters[harvest_index$index_2007_N]
harvest_analysis_Hunters$N_2008 = harvest_2008_N$Hunters[harvest_index$index_2008_N]
harvest_analysis_Hunters$N_2009 = harvest_2009_N$Hunters[harvest_index$index_2009_N]
harvest_analysis_Hunters$N_2010 = harvest_2010_N$Hunters[harvest_index$index_2010_N]
harvest_analysis_Hunters$N_2011 = harvest_2011_N$Hunters[harvest_index$index_2011_N]
harvest_analysis_Hunters$N_2012 = harvest_2012_N$Hunters[harvest_index$index_2012_N]
harvest_analysis_Hunters$N_2013 = harvest_2013_N$Hunters[harvest_index$index_2013_N]
harvest_analysis_Hunters$N_2014 = harvest_2014_N$Hunters[harvest_index$index_2014_N]
harvest_analysis_Hunters$N_2015 = harvest_2015_N$Hunters[harvest_index$index_2015_N]
harvest_analysis_Hunters$N_2016 = harvest_2016_N$Hunters[harvest_index$index_2016_N]
harvest_analysis_Hunters$N_2017 = harvest_2017_N$Hunters[harvest_index$index_2017_N]
harvest_analysis_Hunters$N_2018 = harvest_2018_N$Hunters[harvest_index$index_2018_N]
harvest_analysis_Hunters$N_2019 = harvest_2019_N$Hunters[harvest_index$index_2019_N]
harvest_analysis_Hunters$N_2020 = harvest_2020_N$Hunters[harvest_index$index_2020_N]
harvest_analysis_Hunters$N_2021 = harvest_2021_N$Hunters[harvest_index$index_2021_N]
```

##### Creating Total Non-Residents Harvest Data Frame

```{r}
harvest_analysis_Total_Harvest = data.frame(hd)
colnames(harvest_analysis_Total_Harvest) = c("hunting district")

harvest_analysis_Total_Harvest$N_2004 = harvest_2004_N$Total.Harvest[harvest_index$index_2004_N]
harvest_analysis_Total_Harvest$N_2005 = harvest_2005_N$Total.Harvest[harvest_index$index_2005_N]
harvest_analysis_Total_Harvest$N_2006 = harvest_2006_N$Total.Harvest[harvest_index$index_2006_N]
harvest_analysis_Total_Harvest$N_2007 = harvest_2007_N$Total.Harvest[harvest_index$index_2007_N]
harvest_analysis_Total_Harvest$N_2008 = harvest_2008_N$Total.Harvest[harvest_index$index_2008_N]
harvest_analysis_Total_Harvest$N_2009 = harvest_2009_N$Total.Harvest[harvest_index$index_2009_N]
harvest_analysis_Total_Harvest$N_2010 = harvest_2010_N$Total.Harvest[harvest_index$index_2010_N]
harvest_analysis_Total_Harvest$N_2011 = harvest_2011_N$Total.Harvest[harvest_index$index_2011_N]
harvest_analysis_Total_Harvest$N_2012 = harvest_2012_N$Total.Harvest[harvest_index$index_2012_N]
harvest_analysis_Total_Harvest$N_2013 = harvest_2013_N$Total.Harvest[harvest_index$index_2013_N]
harvest_analysis_Total_Harvest$N_2014 = harvest_2014_N$Total.Harvest[harvest_index$index_2014_N]
harvest_analysis_Total_Harvest$N_2015 = harvest_2015_N$Total.Harvest[harvest_index$index_2015_N]
harvest_analysis_Total_Harvest$N_2016 = harvest_2016_N$Total.Harvest[harvest_index$index_2016_N]
harvest_analysis_Total_Harvest$N_2017 = harvest_2017_N$Total.Harvest[harvest_index$index_2017_N]
harvest_analysis_Total_Harvest$N_2018 = harvest_2018_N$Total.Harvest[harvest_index$index_2018_N]
harvest_analysis_Total_Harvest$N_2019 = harvest_2019_N$Total.Harvest[harvest_index$index_2019_N]
harvest_analysis_Total_Harvest$N_2020 = harvest_2020_N$Total.Harvest[harvest_index$index_2020_N]
harvest_analysis_Total_Harvest$N_2021 = harvest_2021_N$Total.Harvest[harvest_index$index_2021_N]
```

##### Creating Non-Residents Bulls Data Frame

```{r}
harvest_analysis_Bulls = data.frame(hd)
colnames(harvest_analysis_Bulls) = c("hunting district")

harvest_analysis_Bulls$N_2004 = harvest_2004_N$Bulls[harvest_index$index_2004_N]
harvest_analysis_Bulls$N_2005 = harvest_2005_N$Bulls[harvest_index$index_2005_N]
harvest_analysis_Bulls$N_2006 = harvest_2006_N$Bulls[harvest_index$index_2006_N]
harvest_analysis_Bulls$N_2007 = harvest_2007_N$Bulls[harvest_index$index_2007_N]
harvest_analysis_Bulls$N_2008 = harvest_2008_N$Bulls[harvest_index$index_2008_N]
harvest_analysis_Bulls$N_2009 = harvest_2009_N$Bulls[harvest_index$index_2009_N]
harvest_analysis_Bulls$N_2010 = harvest_2010_N$Bulls[harvest_index$index_2010_N]
harvest_analysis_Bulls$N_2011 = harvest_2011_N$Bulls[harvest_index$index_2011_N]
harvest_analysis_Bulls$N_2012 = harvest_2012_N$Bulls[harvest_index$index_2012_N]
harvest_analysis_Bulls$N_2013 = harvest_2013_N$Bulls[harvest_index$index_2013_N]
harvest_analysis_Bulls$N_2014 = harvest_2014_N$Bulls[harvest_index$index_2014_N]
harvest_analysis_Bulls$N_2015 = harvest_2015_N$Bulls[harvest_index$index_2015_N]
harvest_analysis_Bulls$N_2016 = harvest_2016_N$Bulls[harvest_index$index_2016_N]
harvest_analysis_Bulls$N_2017 = harvest_2017_N$Bulls[harvest_index$index_2017_N]
harvest_analysis_Bulls$N_2018 = harvest_2018_N$Bulls[harvest_index$index_2018_N]
harvest_analysis_Bulls$N_2019 = harvest_2019_N$Bulls[harvest_index$index_2019_N]
harvest_analysis_Bulls$N_2020 = harvest_2020_N$Bulls[harvest_index$index_2020_N]
harvest_analysis_Bulls$N_2021 = harvest_2021_N$Bulls[harvest_index$index_2021_N]
```

##### Creating Non-Residents 6 or more points Data Frame

```{r}
harvest_analysis_X6orMorePoints = data.frame(hd)
colnames(harvest_analysis_X6orMorePoints) = c("hunting district")

harvest_analysis_X6orMorePoints$N_2004 = harvest_2004_N$X6.or.More.Points[harvest_index$index_2004_N]
harvest_analysis_X6orMorePoints$N_2005 = harvest_2005_N$X6.or.More.Points[harvest_index$index_2005_N]
harvest_analysis_X6orMorePoints$N_2006 = harvest_2006_N$X6.or.More.Points[harvest_index$index_2006_N]
harvest_analysis_X6orMorePoints$N_2007 = harvest_2007_N$X6.or.More.Points[harvest_index$index_2007_N]
harvest_analysis_X6orMorePoints$N_2008 = harvest_2008_N$X6.or.More.Points[harvest_index$index_2008_N]
harvest_analysis_X6orMorePoints$N_2009 = harvest_2009_N$X6.or.More.Points[harvest_index$index_2009_N]
harvest_analysis_X6orMorePoints$N_2010 = harvest_2010_N$X6.or.More.Points[harvest_index$index_2010_N]
harvest_analysis_X6orMorePoints$N_2011 = harvest_2011_N$X6.or.More.Points[harvest_index$index_2011_N]
harvest_analysis_X6orMorePoints$N_2012 = harvest_2012_N$X6.or.More.Points[harvest_index$index_2012_N]
harvest_analysis_X6orMorePoints$N_2013 = harvest_2013_N$X6.or.More.Points[harvest_index$index_2013_N]
harvest_analysis_X6orMorePoints$N_2014 = harvest_2014_N$X6.or.More.Points[harvest_index$index_2014_N]
harvest_analysis_X6orMorePoints$N_2015 = harvest_2015_N$X6.or.More.Points[harvest_index$index_2015_N]
harvest_analysis_X6orMorePoints$N_2016 = harvest_2016_N$X6.or.More.Points[harvest_index$index_2016_N]
harvest_analysis_X6orMorePoints$N_2017 = harvest_2017_N$X6.or.More.Points[harvest_index$index_2017_N]
harvest_analysis_X6orMorePoints$N_2018 = harvest_2018_N$X6.or.More.Points[harvest_index$index_2018_N]
harvest_analysis_X6orMorePoints$N_2019 = harvest_2019_N$X6.or.More.Points[harvest_index$index_2019_N]
harvest_analysis_X6orMorePoints$N_2020 = harvest_2020_N$X6.or.More.Points[harvest_index$index_2020_N]
harvest_analysis_X6orMorePoints$N_2021 = harvest_2021_N$X6.or.More.Points[harvest_index$index_2021_N]
```



##### Creating Residents Hunters Data Frame

```{r}
harvest_analysis_Hunters$R_2004 = harvest_2004_R$Hunters[harvest_index$index_2004_R]
harvest_analysis_Hunters$R_2005 = harvest_2005_R$Hunters[harvest_index$index_2005_R]
harvest_analysis_Hunters$R_2006 = harvest_2006_R$Hunters[harvest_index$index_2006_R]
harvest_analysis_Hunters$R_2007 = harvest_2007_R$Hunters[harvest_index$index_2007_R]
harvest_analysis_Hunters$R_2008 = harvest_2008_R$Hunters[harvest_index$index_2008_R]
harvest_analysis_Hunters$R_2009 = harvest_2009_R$Hunters[harvest_index$index_2009_R]
harvest_analysis_Hunters$R_2010 = harvest_2010_R$Hunters[harvest_index$index_2010_R]
harvest_analysis_Hunters$R_2011 = harvest_2011_R$Hunters[harvest_index$index_2011_R]
harvest_analysis_Hunters$R_2012 = harvest_2012_R$Hunters[harvest_index$index_2012_R]
harvest_analysis_Hunters$R_2013 = harvest_2013_R$Hunters[harvest_index$index_2013_R]
harvest_analysis_Hunters$R_2014 = harvest_2014_R$Hunters[harvest_index$index_2014_R]
harvest_analysis_Hunters$R_2015 = harvest_2015_R$Hunters[harvest_index$index_2015_R]
harvest_analysis_Hunters$R_2016 = harvest_2016_R$Hunters[harvest_index$index_2016_R]
harvest_analysis_Hunters$R_2017 = harvest_2017_R$Hunters[harvest_index$index_2017_R]
harvest_analysis_Hunters$R_2018 = harvest_2018_R$Hunters[harvest_index$index_2018_R]
harvest_analysis_Hunters$R_2019 = harvest_2019_R$Hunters[harvest_index$index_2019_R]
harvest_analysis_Hunters$R_2020 = harvest_2020_R$Hunters[harvest_index$index_2020_R]
harvest_analysis_Hunters$R_2021 = harvest_2021_R$Hunters[harvest_index$index_2021_R]
```

##### Creating Total Residents Harvest Data Frame

```{r}
harvest_analysis_Total_Harvest$R_2004 = harvest_2004_R$Total.Harvest[harvest_index$index_2004_R]
harvest_analysis_Total_Harvest$R_2005 = harvest_2005_R$Total.Harvest[harvest_index$index_2005_R]
harvest_analysis_Total_Harvest$R_2006 = harvest_2006_R$Total.Harvest[harvest_index$index_2006_R]
harvest_analysis_Total_Harvest$R_2007 = harvest_2007_R$Total.Harvest[harvest_index$index_2007_R]
harvest_analysis_Total_Harvest$R_2008 = harvest_2008_R$Total.Harvest[harvest_index$index_2008_R]
harvest_analysis_Total_Harvest$R_2009 = harvest_2009_R$Total.Harvest[harvest_index$index_2009_R]
harvest_analysis_Total_Harvest$R_2010 = harvest_2010_R$Total.Harvest[harvest_index$index_2010_R]
harvest_analysis_Total_Harvest$R_2011 = harvest_2011_R$Total.Harvest[harvest_index$index_2011_R]
harvest_analysis_Total_Harvest$R_2012 = harvest_2012_R$Total.Harvest[harvest_index$index_2012_R]
harvest_analysis_Total_Harvest$R_2013 = harvest_2013_R$Total.Harvest[harvest_index$index_2013_R]
harvest_analysis_Total_Harvest$R_2014 = harvest_2014_R$Total.Harvest[harvest_index$index_2014_R]
harvest_analysis_Total_Harvest$R_2015 = harvest_2015_R$Total.Harvest[harvest_index$index_2015_R]
harvest_analysis_Total_Harvest$R_2016 = harvest_2016_R$Total.Harvest[harvest_index$index_2016_R]
harvest_analysis_Total_Harvest$R_2017 = harvest_2017_R$Total.Harvest[harvest_index$index_2017_R]
harvest_analysis_Total_Harvest$R_2018 = harvest_2018_R$Total.Harvest[harvest_index$index_2018_R]
harvest_analysis_Total_Harvest$R_2019 = harvest_2019_R$Total.Harvest[harvest_index$index_2019_R]
harvest_analysis_Total_Harvest$R_2020 = harvest_2020_R$Total.Harvest[harvest_index$index_2020_R]
harvest_analysis_Total_Harvest$R_2021 = harvest_2021_R$Total.Harvest[harvest_index$index_2021_R]
```

##### Creating Residents Bulls Data Frame

```{r}
harvest_analysis_Bulls$R_2004 = harvest_2004_R$Bulls[harvest_index$index_2004_R]
harvest_analysis_Bulls$R_2005 = harvest_2005_R$Bulls[harvest_index$index_2005_R]
harvest_analysis_Bulls$R_2006 = harvest_2006_R$Bulls[harvest_index$index_2006_R]
harvest_analysis_Bulls$R_2007 = harvest_2007_R$Bulls[harvest_index$index_2007_R]
harvest_analysis_Bulls$R_2008 = harvest_2008_R$Bulls[harvest_index$index_2008_R]
harvest_analysis_Bulls$R_2009 = harvest_2009_R$Bulls[harvest_index$index_2009_R]
harvest_analysis_Bulls$R_2010 = harvest_2010_R$Bulls[harvest_index$index_2010_R]
harvest_analysis_Bulls$R_2011 = harvest_2011_R$Bulls[harvest_index$index_2011_R]
harvest_analysis_Bulls$R_2012 = harvest_2012_R$Bulls[harvest_index$index_2012_R]
harvest_analysis_Bulls$R_2013 = harvest_2013_R$Bulls[harvest_index$index_2013_R]
harvest_analysis_Bulls$R_2014 = harvest_2014_R$Bulls[harvest_index$index_2014_R]
harvest_analysis_Bulls$R_2015 = harvest_2015_R$Bulls[harvest_index$index_2015_R]
harvest_analysis_Bulls$R_2016 = harvest_2016_R$Bulls[harvest_index$index_2016_R]
harvest_analysis_Bulls$R_2017 = harvest_2017_R$Bulls[harvest_index$index_2017_R]
harvest_analysis_Bulls$R_2018 = harvest_2018_R$Bulls[harvest_index$index_2018_R]
harvest_analysis_Bulls$R_2019 = harvest_2019_R$Bulls[harvest_index$index_2019_R]
harvest_analysis_Bulls$R_2020 = harvest_2020_R$Bulls[harvest_index$index_2020_R]
harvest_analysis_Bulls$R_2021 = harvest_2021_R$Bulls[harvest_index$index_2021_R]
```

##### Creating Residents 6 or more points Data Frame

```{r}
harvest_analysis_X6orMorePoints$R_2004 = harvest_2004_R$X6.or.More.Points[harvest_index$index_2004_R]
harvest_analysis_X6orMorePoints$R_2005 = harvest_2005_R$X6.or.More.Points[harvest_index$index_2005_R]
harvest_analysis_X6orMorePoints$R_2006 = harvest_2006_R$X6.or.More.Points[harvest_index$index_2006_R]
harvest_analysis_X6orMorePoints$R_2007 = harvest_2007_R$X6.or.More.Points[harvest_index$index_2007_R]
harvest_analysis_X6orMorePoints$R_2008 = harvest_2008_R$X6.or.More.Points[harvest_index$index_2008_R]
harvest_analysis_X6orMorePoints$R_2009 = harvest_2009_R$X6.or.More.Points[harvest_index$index_2009_R]
harvest_analysis_X6orMorePoints$R_2010 = harvest_2010_R$X6.or.More.Points[harvest_index$index_2010_R]
harvest_analysis_X6orMorePoints$R_2011 = harvest_2011_R$X6.or.More.Points[harvest_index$index_2011_R]
harvest_analysis_X6orMorePoints$R_2012 = harvest_2012_R$X6.or.More.Points[harvest_index$index_2012_R]
harvest_analysis_X6orMorePoints$R_2013 = harvest_2013_R$X6.or.More.Points[harvest_index$index_2013_R]
harvest_analysis_X6orMorePoints$R_2014 = harvest_2014_R$X6.or.More.Points[harvest_index$index_2014_R]
harvest_analysis_X6orMorePoints$R_2015 = harvest_2015_R$X6.or.More.Points[harvest_index$index_2015_R]
harvest_analysis_X6orMorePoints$R_2016 = harvest_2016_R$X6.or.More.Points[harvest_index$index_2016_R]
harvest_analysis_X6orMorePoints$R_2017 = harvest_2017_R$X6.or.More.Points[harvest_index$index_2017_R]
harvest_analysis_X6orMorePoints$R_2018 = harvest_2018_R$X6.or.More.Points[harvest_index$index_2018_R]
harvest_analysis_X6orMorePoints$R_2019 = harvest_2019_R$X6.or.More.Points[harvest_index$index_2019_R]
harvest_analysis_X6orMorePoints$R_2020 = harvest_2020_R$X6.or.More.Points[harvest_index$index_2020_R]
harvest_analysis_X6orMorePoints$R_2021 = harvest_2021_R$X6.or.More.Points[harvest_index$index_2021_R]
```


##### Generating Graphics for Analysis

```{r}
graphics_analysis = Deer_and_Elk_Hunting_Districts
```

# Exploratory Analysis

##### Non-Resident Hunters Map

```{r}
hunters_summary = data.frame(hd)
colnames(hunters_summary) = c("hunting districts")
hunters_summary$hunters =  rep(0, length(hd))
for(j in 1:length(hd)){
  hunters_summary$hunters[j] = sum(na.omit(harvest_analysis_Hunters[j,2:19]))
}
graphics_analysis$Hunters_Summary = hunters_summary$hunters[match(graphics_analysis$DISTRICT,hunters_summary$`hunting district`)]

plot(graphics_analysis["Hunters_Summary"])

(best_hunters = head(hunters_summary %>% select(`hunting districts`, hunters) %>% arrange(desc(hunters))))
```

##### Non-Resident Harvest Map

```{r}
harvest_summary = data.frame(hd)
colnames(harvest_summary) = c("hunting districts")
harvest_summary$harvests =  rep(0, length(hd))
for(j in 1:length(hd)){
  harvest_summary$harvests[j] = sum(na.omit(harvest_analysis_Total_Harvest[j,2:19]))
}
graphics_analysis$Harvests_Summary = harvest_summary$harvests[match(graphics_analysis$DISTRICT,harvest_summary$`hunting district`)]

plot(graphics_analysis["Harvests_Summary"])

(best_harvest = head(harvest_summary %>% select(`hunting districts`, harvests) %>% arrange(desc(harvests))))
```

##### Non-Resident Bull Harvest Map

```{r}
bulls_summary = data.frame(hd)
colnames(bulls_summary) = c("hunting districts")
bulls_summary$bulls =  rep(0, length(hd))
for(j in 1:length(hd)){
  bulls_summary$bulls[j] = sum(na.omit(harvest_analysis_Bulls[j,2:19]))
}
graphics_analysis$Bulls_Summary = bulls_summary$bulls[match(graphics_analysis$DISTRICT,bulls_summary$`hunting district`)]

plot(graphics_analysis["Bulls_Summary"])

(best_bulls = head(bulls_summary %>% select(`hunting districts`, bulls) %>% arrange(desc(bulls))))
```

##### Non-Resident Bulls w/ 6 or More Points Map

```{r}
x6ormore_summary = data.frame(hd)
colnames(x6ormore_summary) = c("hunting districts")
x6ormore_summary$x6ormore =  rep(0, length(hd))
for(j in 1:length(hd)){
  x6ormore_summary$x6ormore[j] = sum(na.omit(harvest_analysis_X6orMorePoints[j,2:19]))
}
graphics_analysis$X6ormore_Summary = x6ormore_summary$x6ormore[match(graphics_analysis$DISTRICT,x6ormore_summary$`hunting district`)]

plot(graphics_analysis["X6ormore_Summary"])

(best_x6ormore = head(x6ormore_summary %>% select(`hunting districts`, x6ormore) %>% arrange(desc(x6ormore))))
```

##### Non-Resident Harvest Rates

```{r}
harvest_rate_summary = data.frame(hd)
colnames(harvest_rate_summary) = c("hunting districts")
harvest_rate_summary$harvest =  harvest_summary$harvest
harvest_rate_summary$bull_harvest =  bulls_summary$bulls
harvest_rate_summary$x6ormore_harvest =  x6ormore_summary$x6ormore
harvest_rate_summary$hunters = hunters_summary$hunters
harvest_rate_summary$harvest_rate =  harvest_summary$harvest/hunters_summary$hunters
harvest_rate_summary$bull_harvest_rate =  bulls_summary$bulls/hunters_summary$hunters
harvest_rate_summary$x6ormore_harvest_rate =  x6ormore_summary$x6ormore/hunters_summary$hunters


(best_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, harvest_rate) %>% arrange(desc(harvest_rate))))
(best_bull_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, bull_harvest_rate) %>% arrange(desc(bull_harvest_rate))))
(best_x6ormore_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, x6ormore_harvest_rate) %>% arrange(desc(x6ormore_harvest_rate))))
```

##### Resident Hunters Map

```{r}
hunters_summary = data.frame(hd)
colnames(hunters_summary) = c("hunting districts")
hunters_summary$hunters =  rep(0, length(hd))
for(j in 1:length(hd)){
  hunters_summary$hunters[j] = sum(na.omit(harvest_analysis_Hunters[j,20:37]))
}
graphics_analysis$Hunters_Summary = hunters_summary$hunters[match(graphics_analysis$DISTRICT,hunters_summary$`hunting district`)]

plot(graphics_analysis["Hunters_Summary"])

(best_hunters = head(hunters_summary %>% select(`hunting districts`, hunters) %>% arrange(desc(hunters))))
```

##### Resident Harvest Map

```{r}
harvest_summary = data.frame(hd)
colnames(harvest_summary) = c("hunting districts")
harvest_summary$harvests =  rep(0, length(hd))
for(j in 1:length(hd)){
  harvest_summary$harvests[j] = sum(na.omit(harvest_analysis_Total_Harvest[j,20:37]))
}
graphics_analysis$Harvests_Summary = harvest_summary$harvests[match(graphics_analysis$DISTRICT,harvest_summary$`hunting district`)]

plot(graphics_analysis["Harvests_Summary"])

(best_harvest = head(harvest_summary %>% select(`hunting districts`, harvests) %>% arrange(desc(harvests))))
```

##### Resident Bull Harvest Map

```{r}
bulls_summary = data.frame(hd)
colnames(bulls_summary) = c("hunting districts")
bulls_summary$bulls =  rep(0, length(hd))
for(j in 1:length(hd)){
  bulls_summary$bulls[j] = sum(na.omit(harvest_analysis_Bulls[j,20:37]))
}
graphics_analysis$Bulls_Summary = bulls_summary$bulls[match(graphics_analysis$DISTRICT,bulls_summary$`hunting district`)]

plot(graphics_analysis["Bulls_Summary"])

(best_bulls = head(bulls_summary %>% select(`hunting districts`, bulls) %>% arrange(desc(bulls))))
```

##### Resident Bulls w/ 6 or More Points Map

```{r}
x6ormore_summary = data.frame(hd)
colnames(x6ormore_summary) = c("hunting districts")
x6ormore_summary$x6ormore =  rep(0, length(hd))
for(j in 1:length(hd)){
  x6ormore_summary$x6ormore[j] = sum(na.omit(harvest_analysis_X6orMorePoints[j,20:37]))
}
graphics_analysis$X6ormore_Summary = x6ormore_summary$x6ormore[match(graphics_analysis$DISTRICT,x6ormore_summary$`hunting district`)]

plot(graphics_analysis["X6ormore_Summary"])

(best_x6ormore = head(x6ormore_summary %>% select(`hunting districts`, x6ormore) %>% arrange(desc(x6ormore))))
```

##### Resident Harvest Rates

```{r}
harvest_rate_summary = data.frame(hd)
colnames(harvest_rate_summary) = c("hunting districts")
harvest_rate_summary$harvest =  harvest_summary$harvest
harvest_rate_summary$bull_harvest =  bulls_summary$bulls
harvest_rate_summary$x6ormore_harvest =  x6ormore_summary$x6ormore
harvest_rate_summary$hunters = hunters_summary$hunters
harvest_rate_summary$harvest_rate =  harvest_summary$harvest/hunters_summary$hunters
harvest_rate_summary$bull_harvest_rate =  bulls_summary$bulls/hunters_summary$hunters
harvest_rate_summary$x6ormore_harvest_rate =  x6ormore_summary$x6ormore/hunters_summary$hunters


(best_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, harvest_rate) %>% arrange(desc(harvest_rate))))
(best_bull_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, bull_harvest_rate) %>% arrange(desc(bull_harvest_rate))))
(best_x6ormore_harvest_rate = head(harvest_rate_summary %>% select(`hunting districts`, x6ormore_harvest_rate) %>% arrange(desc(x6ormore_harvest_rate))))
```
